Implementing DNS in C0

### 2017-11-17 proposal.tex
Citation changed for dnsperf.

For performance analysis, we plan to evaluate our nameserver for latency and throughput, as these appear to be the most important metrics for \Kwd{DNS} performance. We plan to do this using one of two pieces of software\footnote{https://github.com/cobblau/dnsperf, https://github.com/nominum/dnsperf} (confusingly, both named \texttt{dnsperf}), which read queries from a file and then send these requests to a nameserver. The latter seems better-suited to our needs, as the former appears to not give latency information in a useful fashion. We will compare our results (at various load levels) to existing \Kwd{DNS} software (though we have yet to determine which specific software to take as our baseline). One remaining difficulty in evaluation lies in figuring out what sort of query workload to use --- the performance analysis tools we have looked at suggest using an input file with somewhere on the order of one million queries, which is more than can feasibly be generated by hand. However, there does not appear to be a standard benchmark for this testing as there are for many other systems. We will likely generate large test files in a randomized way, but do not have a good sense of how to make these files accurately reflect realistic usage.

>>>>

For performance analysis, we plan to evaluate our nameserver for latency and throughput, as these appear to be the most important metrics for \Kwd{DNS} performance. We plan to do this using one of two pieces of software\cite{github:dnsperf1, github:dnsperf2} (confusingly, both named \texttt{dnsperf}), which read queries from a file and then send these requests to a nameserver. The latter seems better-suited to our needs, as the former appears to not give latency information in a useful fashion. We will compare our results (at various load levels) to existing \Kwd{DNS} software (though we have yet to determine which specific software to take as our baseline). One remaining difficulty in evaluation lies in figuring out what sort of query workload to use --- the performance analysis tools we have looked at suggest using an input file with somewhere on the order of one million queries, which is more than can feasibly be generated by hand. However, there does not appear to be a standard benchmark for this testing as there are for many other systems. We will likely generate large test files in a randomized way, but do not have a good sense of how to make these files accurately reflect realistic usage.
